\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex
added mention of wiegand connection.
Added initial background

\section{Background \& Significance}

@@

\section{Research Design \& Methodology}
Our research seeks to analyze the security posture of the readers as they would appear in a customer environment. As such, our research design follows a quasi-experimental structure, meaning only pre-existing configurations of the reader will be studied. Setup of the reader for testing will require connecting the power and ground wires to a 12v power source and the D0, D1, and tamper wires to a raspberry pi. Interfacing with a raspberry pi allows researchers flexible access to perform multiple different tasks such as collecting data or changing configurations. Researchers may also choose to set up the BlueDiamond mobile app to allow the ability for testing bluetooth traffic sent and received by the device. The attack vector serves as a variable in this equation as its outcome can be scored against others using a common standard. Observations of consistency, difficulty, and threat level will allow us to score each attack vector using the Common Vulnerability Scoring System (CVSS) \cite{cvss}.

>>>>

\section{Background \& Significance}
Throughout history, people have tried to gain access restricted areas. \cite{lockpickinghistory}  Locks were created in order to restrict access, but locksmiths were often skeptical of their inventions, and if they could be bypassed.  The first documented case of lock picking was a challenge released by Joseph Bramah, an Enlish locksmith.  Bramah had just developed his so called safety lock.  His lock had safety features that he believed to be completely secure.  Obviously, nothing is ever completely secure, but Bramah put it to the test by announcing a contest.  Anyone who could break into his new creation would net a cool sum of 20,000 pounds.

While the Bramah challenge was still in place, another locksmith caught wind of Bramah's idea.  Jeremiah Chubb built a lock that would alert an owner if any sort of picking had been detected.  He too, announced a challnge.  An American Locksmith named A.C. Hobbs took up the challenge, and had it open within an hour of touching the lock.  However, that wasn't the only challenge he accepted.  Chubb took a trip over to Hobbs' locksmithing shop, and 70 years later, picked the Bramah security lock.

New technology leads to new innovation.  Almost overnight, businesses and organizations started using electronic locking systems for their ease of use and simplicity in granting or denying access.  Granting access to a building is as simple as a few button clicks.  For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to re-key a lock every single time an employee leaves the organization.

Lock Picking may be a thing of the past, but the security of electronic locks still need to be audited.  With most RFID-based systems, like those in locks, cloning cards is easier than ever due to new tools like the ProxMark RFID toolkit.\cite{7945583}  Even though the physical element of locks and lock picking may not stay the same with these newer electronic locking systems, the spirit stays alive in the hacking community.  These locks aren't invulnerable, but security professionals can certainly help bring them to the point where they can withstand basic attacks.

@@

\section{Research Design \& Methodology}
Our research seeks to analyze the security posture of the readers as they would appear in a customer environment. As such, our research design follows a quasi-experimental structure, meaning only pre-existing configurations of the reader will be studied. Setup of the reader for testing will require connecting the power and ground wires to a 12v power source and the D0, D1, and tamper wires to a raspberry pi. Interfacing with a raspberry pi allows researchers flexible access to perform multiple different tasks such as collecting data or changing configurations. Our proposed connection will allow for easy analysis of the Wiegand hardware within the device. Researchers may also choose to set up the BlueDiamond mobile app to allow the ability for testing bluetooth traffic sent and received by the device. The attack vector serves as a variable in this equation as its outcome can be scored against others using a common standard. Observations of consistency, difficulty, and threat level will allow us to score each attack vector using the Common Vulnerability Scoring System (CVSS) \cite{cvss}.
